---
title: "BST5220 multilevel HW1"
author: "Miao Cai [miao.cai@slu.edu](miao.cai@slu.edu)"
date: "2/4/2019"
output:
  word_document: default
  pdf_document: default
linkcolor: blue
subtitle: Due Wednesday by 12:00 pm, 2/11
link-citations: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


You will first need to run the SAS code (homework1_data.sas) to create the SAS data set. The purpose of this study is to assess how job-related stress is related to hospital size (0=small, 1=medium, 2=large) and nurse’s job experience (years). Data are from nurses working in 25 hospitals. In each hospital, a sample of about 40 nurses is selected and given a test that measures job-related stress (coded on a scale of 0-7). 

1.	Identify the type of the data structure (cross-sectional clustered, longitudinal, or clustered longitudinal).
2.	Identify the variables at each level. 
3.	Graphically examine the association between job stress and nurse’s experience within each hospital. Refer to slides 8-11, lecture 2.
4.	Use the model building strategies discussed in lecture 3 to select the best model for the data


```{r}
dat = rio::import("data/a1.sas7bdat")
head(dat)
```

1. This is a cross-sectional clustered data struture
2. Variables at each level:
  + Hospital level: hospital, hospital_size
  + Nurse level: stress, experience
3. Graphically examine the association between job stress and nurse’s experience within each hospital

```{r fig.width=10, fig.height=12}
pacman::p_load(tidyverse)

dat %>% 
  ggplot(aes(experience, stress,)) + geom_point(alpha = 0.5) + geom_jitter() + 
  geom_smooth(method = "lm", se=FALSE, color="blue") + 
  facet_wrap(.~hospital, ncol = 5)
```

```{r results='hide', eval=FALSE}
pacman::p_load(rstanarm, brms)

fit0 = stan_lmer(stress ~ (1|hospital), data = dat,
                 chains = 1, iter = 1000, warmup = 500)
fitbrms0 = brm(
  stress ~ (1|hospital), data = dat,
                 chains = 1, iter = 1000, warmup = 500
)
```
```{r}
summary(fit0)
```


